Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses

### 2014-12-07 doc/slides/hong+eisner.TLT13.slides.tex
fixed the slack in the ILP slides. Added roots to example parses.

\section{Motivation}
\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item Such a corpus could be automatically annotated using Integer Linear Programming
  \end{itemize}
}

\section{Motivation}
\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item Such a corpus could be automatically annotated using Integer Linear Programming
    \item We explored whether the Link Grammar could be adapted for this purpose.
  \end{itemize}
}

\section{Motivation}
\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item Such a corpus could be automatically annotated using Integer Linear Programming
    \item We explored whether the Link Grammar could be adapted for this purpose.
    \item The results of this are mixed, but provides a good case study.
  \end{itemize}
}

@@

\subsection{Control}
\frame{\frametitle{Control}
  \begin{figure}
    \begin{dependency}
      \begin{deptext}
        Jill \& likes \& to \& skip \\
      \end{deptext}
      \depedge[edge above, thick, hide label]{2}{1}{}
      \depedge[edge below, ultra thick, hide label, edge style = {purple}, edge unit distance = 1.5ex]{4}{1}{}
      \depedge[edge above, thick, hide label]{2}{3}{}
      \depedge[edge above, thick, hide label]{3}{4}{}
    \end{dependency}
    \caption*{Jill is the subject of two verbs}
  \end{figure}

  \begin{figure}
    \begin{dependency}
      \begin{deptext}
        Jill \& persuaded \& Jack \& to \& skip \\
      \end{deptext}
      \depedge[edge above, thick, hide label]{2}{1}{}
      \depedge[edge above, thick, hide label]{2}{3}{}
      \depedge[edge above, thick, hide label]{3}{4}{}
      \depedge[edge above, thick, hide label]{4}{5}{}
      \depedge[edge below, ultra thick, hide label, edge style = {purple}, edge unit distance = 1.5ex]{3}{5}{}
    \end{dependency}
    \caption*{Jack is the object of one verb and the subject of another}
  \end{figure}
}

\subsection{Relativization}
\frame{\frametitle{Relativization}
  \begin{figure}
    \begin{dependency}
      \begin{deptext}
        The \& boy \& that \& Jill \& skipped \& with \& fell \& down \\
      \end{deptext}
      \depedge[edge above, thick, hide label]{2}{1}{}
      \depedge[edge above, thick, hide label]{2}{3}{}
      \depedge[edge above, thick, hide label]{3}{4}{}
      \depedge[edge above, thick, hide label]{4}{5}{}
      \depedge[edge above, thick, hide label]{5}{6}{}
      \depedge[edge above, thick, hide label]{2}{7}{}
      \depedge[edge above, thick, hide label]{7}{8}{}
      \depedge[edge below, ultra thick, hide label, edge style = {purple}, edge unit distance = 1.5ex]{6}{2}{}
    \end{dependency}
    \caption*{The boy is the object of ``with'' as well as the subject of ``fell''.}
  \end{figure}
}

\subsection{Conjunction}
\frame{\frametitle{Conjunction}
  \begin{figure}
    \begin{dependency}
      \begin{deptext}
        Jack \& and \& Jill \& went \& up \& the \& hill \\
      \end{deptext}
      \depedge[edge above, thick, hide label]{2}{1}{}
      \depedge[edge above, thick, hide label]{2}{3}{}
      \depedge[edge above, thick, hide label]{4}{2}{}
      \depedge[edge above, thick, hide label]{4}{5}{}
      \depedge[edge above, thick, hide label]{5}{7}{}
      \depedge[edge above, thick, hide label]{7}{6}{}

@@

\frame{\frametitle{Consistence of Directionalized Links}
\begin{itemize}
  \item[] Consistency of Directionalized Links
    \begin{align}\label{direction+slack}
      x_{ij} &\leq r_L + s_{ij} &
      x_{ji} &\leq \ell_L + s_{ij}
    \end{align}

>>>>

\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item Such a corpus could be automatically annotated using Integer Linear Programming
  \end{itemize}
}

\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item Such a corpus could be automatically annotated using Integer Linear Programming
    \item We explored whether the Link Grammar could be adapted for this purpose.
  \end{itemize}
}

\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item Such a corpus could be automatically annotated using Integer Linear Programming
    \item We explored whether the Link Grammar could be adapted for this purpose.
    \item The results of this are mixed, but provides a good case study.
  \end{itemize}
}

@@

\subsection{Control}
\frame{\frametitle{Control}
  \begin{figure}
    \begin{dependency}
      \begin{deptext}
        Jill \& likes \& to \& skip \\
      \end{deptext}
      \deproot[edge above, thick, hide label, edge unit distance = 1.5ex]{2}{}
      \depedge[edge above, thick, hide label]{2}{1}{}
      \depedge[edge below, ultra thick, hide label, edge style = {purple}, edge unit distance = 1.2ex]{4}{1}{}
      \depedge[edge above, thick, hide label]{2}{3}{}
      \depedge[edge above, thick, hide label]{3}{4}{}
    \end{dependency}
    \caption*{Jill is the subject of two verbs}
  \end{figure}

  \begin{figure}
    \begin{dependency}
      \begin{deptext}
        Jill \& persuaded \& Jack \& to \& skip \\
      \end{deptext}
      \deproot[edge above, thick, hide label, edge unit distance = 1.5ex]{2}{}
      \depedge[edge above, thick, hide label]{2}{1}{}
      \depedge[edge above, thick, hide label]{2}{3}{}
      \depedge[edge above, thick, hide label]{3}{4}{}
      \depedge[edge above, thick, hide label]{4}{5}{}
      \depedge[edge below, ultra thick, hide label, edge style = {purple}, edge unit distance = 1.5ex]{3}{5}{}
    \end{dependency}
    \caption*{Jack is the object of one verb and the subject of another}
  \end{figure}
}

\subsection{Relativization}
\frame{\frametitle{Relativization}
  \begin{figure}
    \begin{dependency}
      \begin{deptext}
        The \& boy \& that \& Jill \& skipped \& with \& fell \& down \\
      \end{deptext}
      \deproot[edge above, thick, hide label, edge unit distance = 1.5ex]{7}{}
      \depedge[edge above, thick, hide label]{2}{1}{}
      \depedge[edge above, thick, hide label]{2}{3}{}
      \depedge[edge above, thick, hide label]{3}{5}{}
      \depedge[edge above, thick, hide label]{5}{4}{}
      \depedge[edge above, thick, hide label]{5}{6}{}
      \depedge[edge above, thick, hide label, edge unit distance = 1.8ex]{7}{2}{}
      \depedge[edge above, thick, hide label]{7}{8}{}
      \depedge[edge below, ultra thick, hide label, edge style = {purple}, edge unit distance = 1.5ex]{6}{2}{}
    \end{dependency}
    \caption*{The boy is the object of ``with'' as well as the subject of ``fell''.}
  \end{figure}
}

\subsection{Conjunction}
\frame{\frametitle{Conjunction}
  \begin{figure}
    \begin{dependency}
      \begin{deptext}
        Jack \& and \& Jill \& went \& up \& the \& hill \\
      \end{deptext}
      \deproot[edge above, thick, hide label, edge unit distance = 1.5ex]{4}{}
      \depedge[edge above, thick, hide label]{2}{1}{}
      \depedge[edge above, thick, hide label]{2}{3}{}
      \depedge[edge above, thick, hide label]{4}{2}{}
      \depedge[edge above, thick, hide label]{4}{5}{}
      \depedge[edge above, thick, hide label]{5}{7}{}
      \depedge[edge above, thick, hide label]{7}{6}{}

@@

\frame{\frametitle{Consistence of Directionalized Links}
\begin{itemize}
  \item[] Consistency of Directionalized Links
    \begin{align}\label{direction+slack}
      x_{ij} &\leq r_L &
      x_{ji} &\leq \ell_L 
    \end{align}
